scRNAseq benchmark in want of a title

### 2019-11-29 bmc_article.tex
Updates from Overleaf

We next investigated the step of dimensionality reduction, comparing in particular Seurat's PCA, GLM-PCA \citep{townesGlmpca2019}, and a two-step PCA procedure in which cells are first clustered in rough clusters according to a standard PCA, a new PCA is performed on each, and the main components of the two are put together (see methods). Seurat's default PCA weighs the cell embeddings by the variance of each component, so we also tested the impact of this weighting with each method.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{{main_figures/dr_files/figure-html/unnamed-chunk-2-1.png}}
    \caption{Evaluation of the dimensionality reduction strategies.}
    \label{fig:figure7}
\end{figure}

\subsubsection*{Estimating dimension}

>>>>

We next investigated the step of dimensionality reduction, comparing in particular Seurat's PCA, scran's denoise PCA, and GLM-PCA \citep{townesGlmpca2019}, combined (where relevant) with sctransform normalization. Seurat's default PCA weighs the cell embeddings by the variance of each component, so we also tested the impact of this weighting with each method.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{{main_figures/dr_files/figure-html/dimred-1.png}}
    \caption{\textbf{Evaluation of the dimensionality reduction strategies. A:} Average silhouette width per subpopulation according to various normalization and dimension reductions. \textbf{B:} Clustering accuracy , mean proportion of the variance in the first 5 components explained by real subpopulations (center), and median ARI of the resulting clustering (right).}
    \label{fig:figure7}
\end{figure}

\subsubsection*{Estimating the number of dimensions}
